---
title: "Shiny Assignment"
output:
  pdf_document: default
  html_document: default
date: "2024-11-15"
---
# Shiny Assignment

## Exercise 2.3.5:

### Question 1

```{r}
library(shiny)

ui <- fluidPage(
  verbatimTextOutput("summary_output")
)

server <- function(input, output, session) {
  output$summary_output <- renderPrint({
    summary(mtcars)
  })
}

shinyApp(ui, server)
```

### Question 2:
```{r}
ui <- fluidPage(
  textOutput("greeting_output")
)

server <- function(input, output, session) {
  output$greeting_output <- renderText({
    "Good morning!"
  })
}

shinyApp(ui, server)
```

### Question 3:

```{r}
ui <- fluidPage(
  verbatimTextOutput("ttest_output")
)

server <- function(input, output, session) {
  output$ttest_output <- renderPrint({
    t.test(1:5, 2:6)
  })
}

shinyApp(ui, server)
```

### Question 4:

```{r}
ui <- fluidPage(
  verbatimTextOutput("lm_output")
)

server <- function(input, output, session) {
  output$lm_output <- renderPrint({
    str(lm(mpg ~ wt, data = mtcars))
  })
}

shinyApp(ui, server)
```

## Exercise 3.3.6:

### Question 1:

server1 <- function(input, output, server) {
  input$greeting <- renderText(paste0("Hello ", name))
}
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)

server1 <- function(input, output, server) {
  output$greeting <- renderText(paste0("Hello ", input$name))
}
shinyApp(ui, server1)
```

server2 <- function(input, output, server) {
  greeting <- paste0("Hello ", input$name)
  output$greeting <- renderText(greeting)
}

```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
server2 <- function(input, output, server) {
  greeting <- reactive({
    paste("Hello ", input$name)})
  output$greeting <- renderText(greeting())
}
shinyApp(ui, server2)

```

server3 <- function(input, output, server) {
  output$greting <- paste0("Hello", input$name)
}

```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
server3 <- function(input, output, server) {
  output$greeting <- renderText(paste0("Hello ", input$name))
}
shinyApp(ui, server3)
```

### Question 2:


server1 <- function(input, output, session) {
  c <- reactive(input$a + input$b)
  e <- reactive(c() + input$d)
  output$f <- renderText(e())
}

(input$a,input$b) ----- c
(c,input$d) ------ e
e ------ output$f

server2 <- function(input, output, session) {
  x <- reactive(input$x1 + input$x2 + input$x3)
  y <- reactive(input$y1 + input$y2)
  output$z <- renderText(x() / y())
}

(input$x1,input$x2,input$x3)----x
(input$y1,input$y2) -----y
(x,y) ---- output$z

server3 <- function(input, output, session) {
  d <- reactive(c() ^ input$d)
  a <- reactive(input$a * 10)
  c <- reactive(b() / input$c)
  b <- reactive(a() + input$b)
}

(input$d, c) ------ d
(input$a) ---- a
(b, input$c) ---- c
(a,b) ----- b

### Question 3:
 Why will this code fail?

var <- reactive(df[[input$var]])
range <- reactive(range(var(), na.rm = TRUE))
Why are range() and var() bad names for reactive?

Because range() and var() are also function in R which is not unique for reactive!


## Exercise 4.8:

### Question 1:

```{r}
library(vroom)
library(tidyverse)

# Directory setup and data download
dir.create("neiss_data")
download_file <- function(name) {
  base_url <- "https://raw.github.com/hadley/mastering-shiny/main/neiss/"
  download.file(paste0(base_url, name), paste0("neiss_data/", name), quiet = TRUE)
}
download_file("injuries.tsv.gz")
download_file("population.tsv")
download_file("products.tsv")

# Load data
injuries <- vroom::vroom("neiss_data/injuries.tsv.gz")
products <- vroom::vroom("neiss_data/products.tsv")
population <- vroom::vroom("neiss_data/population.tsv")

# Helper function to summarize data
get_top_rows <- function(data, variable, rows = 5) {
  data |>
    mutate({{ variable }} := fct_lump(fct_infreq({{ variable }}), n = rows)) |>
    group_by({{ variable }}) |>
    summarise(n = sum(weight))
}

# Set product codes for UI choices
product_choices <- setNames(products$prod_code, products$title)

# UI layout
ui <- fluidPage(
  fluidRow(
    column(8, selectInput("product", "Select Product", choices = product_choices, width = "100%")),
    column(2, selectInput("y_axis", "Y Axis", choices = c("rate", "count")))
  ),
  fluidRow(
    column(4, tableOutput("diag_table")),
    column(4, tableOutput("body_table")),
    column(4, tableOutput("location_table"))
  ),
  fluidRow(
    column(12, plotOutput("age_sex_plot"))
  ),
  fluidRow(
    column(2, actionButton("tell_story", "Tell a Story")),
    column(10, textOutput("narrative_text"))
  )
)

# Server logic
server <- function(input, output, session) {
  filter_data <- reactive({
    injuries |> filter(prod_code == input$product)
  })

  output$diag_table <- renderTable({
    get_top_rows(filter_data(), diag)
  })

  output$body_table <- renderTable({
    get_top_rows(filter_data(), body_part)
  })

  output$location_table <- renderTable({
    get_top_rows(filter_data(), location)
  })

  create_summary <- reactive({
    filter_data() |>
      count(age, sex, wt = weight) |>
      left_join(population, by = c("age", "sex")) |>
      mutate(rate = n / population * 1e4)
  })

  output$age_sex_plot <- renderPlot({
    summary <- create_summary()
    if (input$y_axis == "count") {
      ggplot(summary, aes(age, n, colour = sex)) +
        geom_line() +
        labs(y = "Number of Injuries")
    } else {
      ggplot(summary, aes(age, rate, colour = sex)) +
        geom_line(na.rm = TRUE) +
        labs(y = "Injury Rate per 10,000 People")
    }
  })

  pick_narrative <- eventReactive(input$tell_story, {
    filter_data() |> pull(narrative) |> sample(1)
  })

  output$narrative_text <- renderText({
    pick_narrative()
  })
}

# Run the app
shinyApp(ui, server)

```


### Question 2:

```{r}
ui <- fluidPage(
  fluidRow(
    column(8, selectInput("product", "Select Product",
                          choices = setNames(products$prod_code, products$title),
                          width = "100%")),
    column(2, checkboxInput("flip_order", "Flip Order", value = FALSE))
  ),
  fluidRow(
    column(4, tableOutput("diag_table"))
  )
)

server <- function(input, output, session) {
  filtered_data <- reactive({
    injuries |> filter(prod_code == input$product)
  })

  output$diag_table <- renderTable({
    if (input$flip_order) {
      # Flipped Order
      filtered_data() |>
        mutate(diag = fct_infreq(fct_lump(diag, n = 5))) |>
        group_by(diag) |>
        summarise(count = sum(weight))
    } else {
      # Original Order
      filtered_data() |>
        mutate(diag = fct_lump(fct_infreq(diag), n = 5)) |>
        group_by(diag) |>
        summarise(count = sum(weight))
    }
  })
}

shinyApp(ui, server)

```

### Question 3:

```{r}
library(shiny)
library(vroom)
library(tidyverse)

# Load data
injuries <- vroom::vroom("neiss_data/injuries.tsv.gz")
products <- vroom::vroom("neiss_data/products.tsv")
population <- vroom::vroom("neiss_data/population.tsv")

# Helper function to summarize data
summarize_top <- function(data, variable, rows = 5) {
  data |>
    mutate({{ variable }} := fct_lump(fct_infreq({{ variable }}), n = rows)) |>
    group_by({{ variable }}) |>
    summarise(count = sum(weight))
}

# UI
ui <- fluidPage(
  fluidRow(
    column(8, selectInput("product", "Select Product",
                          choices = setNames(products$prod_code, products$title),
                          width = "100%")),
    column(2, numericInput("rows", "Rows to Display", value = 5, min = 1, max = 20))
  ),
  fluidRow(
    column(4, tableOutput("diagnosis_table")),
    column(4, tableOutput("body_table")),
    column(4, tableOutput("location_table"))
  ),
  fluidRow(column(12, plotOutput("age_sex_plot")))
)

# Server
server <- function(input, output, session) {
  filtered_data <- reactive({
    injuries |> filter(prod_code == input$product)
  })

  output$diagnosis_table <- renderTable({
    summarize_top(filtered_data(), diag, rows = input$rows)
  })

  output$body_table <- renderTable({
    summarize_top(filtered_data(), body_part, rows = input$rows)
  })

  output$location_table <- renderTable({
    summarize_top(filtered_data(), location, rows = input$rows)
  })

  summary_plot <- reactive({
    filtered_data() |>
      count(age, sex, wt = weight) |>
      left_join(population, by = c("age", "sex")) |>
      mutate(rate = n / population * 1e4)
  })

  output$age_sex_plot <- renderPlot({
    ggplot(summary_plot(), aes(age, rate, color = sex)) +
      geom_line() +
      labs(y = "Injury Rate per 10,000 People")
  })
}

# Run the app
shinyApp(ui, server)

```

### Question 4:

```{r}
library(shiny)
library(vroom)
library(tidyverse)

# Load data
injuries <- vroom::vroom("neiss_data/injuries.tsv.gz")
products <- vroom::vroom("neiss_data/products.tsv")
population <- vroom::vroom("neiss_data/population.tsv")

# Helper function to summarize data
summarize_top <- function(data, variable, rows = 5) {
  data |>
    mutate({{ variable }} := fct_lump(fct_infreq({{ variable }}), n = rows)) |>
    group_by({{ variable }}) |>
    summarise(count = sum(weight))
}

# UI
ui <- fluidPage(
  fluidRow(
    column(8, selectInput("product", "Select Product",
                          choices = setNames(products$prod_code, products$title),
                          width = "100%")),
    column(2, numericInput("rows", "Rows to Display", value = 5, min = 1, max = 20))
  ),
  fluidRow(
    column(4, tableOutput("diagnosis_table")),
    column(4, tableOutput("body_table")),
    column(4, tableOutput("location_table"))
  ),
  fluidRow(
    column(12, plotOutput("age_sex_plot"))
  ),
  fluidRow(
    column(2, actionButton("prev", "Previous")),
    column(2, actionButton("next", "Next")),
    column(8, textOutput("narrative_output"))
  )
)

# Server
server <- function(input, output, session) {
  filtered_data <- reactive({
    injuries |> filter(prod_code == input$product)
  })

  output$diagnosis_table <- renderTable({
    summarize_top(filtered_data(), diag, rows = input$rows)
  })

  output$body_table <- renderTable({
    summarize_top(filtered_data(), body_part, rows = input$rows)
  })

  output$location_table <- renderTable({
    summarize_top(filtered_data(), location, rows = input$rows)
  })

  summary_plot <- reactive({
    filtered_data() |>
      count(age, sex, wt = weight) |>
      left_join(population, by = c("age", "sex")) |>
      mutate(rate = n / population * 1e4)
  })

  output$age_sex_plot <- renderPlot({
    ggplot(summary_plot(), aes(age, rate, color = sex)) +
      geom_line() +
      labs(y = "Injury Rate per 10,000 People")
  })

  # Reactive value for narrative index
  narrative_index <- reactiveVal(1)

  # Update index when Next button is clicked
  observeEvent(input$next, {
    new_index <- narrative_index() + 1
    if (new_index > nrow(filtered_data())) {
      new_index <- 1  # Wrap around to the first narrative
    }
    narrative_index(new_index)
  })

  # Update index when Previous button is clicked
  observeEvent(input$prev, {
    new_index <- narrative_index() - 1
    if (new_index < 1) {
      new_index <- nrow(filtered_data())  # Wrap around to the last narrative
    }
    narrative_index(new_index)
  })

  # Display the current narrative
  output$narrative_output <- renderText({
    selected_data <- filtered_data()
    if (nrow(selected_data) == 0) {
      "No narratives available for the selected product."
    } else {
      selected_data$narrative[narrative_index()]
    }
  })
}

# Run the app
shinyApp(ui, server)

```

